Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-10 code/rmarkdown/article.Rmd
+ article fixes
Former-commit-id: 68074f643424c679603091286768045e7e9f377b

## Results
<!-- summary of methods -->
We successfully mapped the main spatial patterns of adaptive (if present) and neutral variation for each of the 26 species. The outlier detection methods detected adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` species. Generally, two outlier detection methods gave fairly consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD). Of the species that were associated with adaptive genetic variation, only a few loci were detected as under selection (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci under selection, we used NMDS analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. For all species in which we detected adaptive loci, only a couple of continuous dimensions were needed to sufficiently describe their patterns of adaptive genetic variation (Table S2). On the other hand, a few additional continuous dimensions were often needed to describe their patterns of neutral genetic variation (minimum $K = `r min(neutral.k)`$; mean $K = `r round(mean(neutral.k),2)`$; max $K = `r max(neutral.k)`$; Table S2). The ordinations resulting from the NMDS analyses were used to construct an adaptive (if present) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S29--S54) generally show patterns of spatial auto-correlation--especially the adaptive genetic spaces (eg.XXXX; SXX). Additionally, most species show east-west patterns in their intra-specific genetic variation (eg. XXXX; SXXX).

>>>>

## Results
<!-- summary of methods -->
We successfully mapped the main spatial patterns of adaptive (if present) and neutral variation for each of the 26 species. The outlier detection methods detected adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` species. Generally, two outlier detection methods gave fairly consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD). Of the species that were associated with adaptive genetic variation, only a few loci were detected as under selection (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci under selection, we used NMDS analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. For all species in which we detected adaptive loci, only a couple of continuous dimensions were needed to sufficiently describe their patterns of adaptive genetic variation (Table S2). On the other hand, a few additional continuous dimensions were often needed to describe their patterns of neutral genetic variation (minimum $K = `r min(neutral.k)`$; mean $K = `r round(mean(neutral.k),2)`$; max $K = `r max(neutral.k)`$; Table S2). The ordinations resulting from the NMDS analyses were used to construct an adaptive (if present) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S29--S54) generally show patterns of spatial auto-correlation--especially the adaptive genetic spaces (eg. _Cerastium uniflorum_ and _Dryas octopetala_). Additionally, most species show east-west patterns in their intra-specific genetic variation (eg. _Peucedanum ostruthium_ and _Phyteuma betonicifolium_).
